### 2021-05-10 docs/manuscript/PLOS-MSc-Thesis.tex
Improve Fig8 legend

\begin{figure}[!h]
 \includegraphics[width=\textwidth]{figures/results/Fig8}
 \caption{\bf Expression dynamics of topology 9.}
 A: Network topology number 9. B: Spatiotemporal expression profile of a GRN
 with topology 9.
 \label{fig:topol9}
\end{figure}

>>>>

\begin{figure}[!h]
 \includegraphics[width=\textwidth]{figures/results/Fig8}
 \caption{\bf Expression dynamics of topology 9.}
 (A) Network topology number 9. Although this topology consists only of two
 genes, it display a striped pattern of gene expression for both of them as
 can be observed in (B). (B) Spatiotemporal expression profile of a GRN
 with topology 9. Gene \textbf{B} is not shown as it was lost in this topology
 in the evolutionary process simulated by the genetic algorithm.
 \label{fig:topol9}
\end{figure}
